### 2017-04-05 paper/modes.tex
commenting comments

Forking OS processes to run test jobs is a common feature of build
systems as to obtain parallelism at the machine space (see
Figure~\ref{fig:levels}).  For Java-based systems (e.g., Maven and
Ant), this amounts to spawning one JVM instance (per process) per CPU,
on a machine with potentially many virtual CPUs, and aggregating
corresponding results when jobs finish.  Note that forking can only be
combined with configuration \SeqClassParMeth{} (see
Section~\ref{sec:frameworks}) as Maven only accepts one test class at
a time per forked process.\Mar{$\leftarrow$Are you sure about this?
  It seems silly.  Maybe, the rationale is to ``keep design
  simple''.}\Jbc{I'm sure. in addition to keep design simple, I feel
  like this was initially conceived to run tests in isolation}
To attenuate the non-trivial cost of spawning new processes and JVMs on
every test class, Maven offers an option to reuse the
JVM.\Mar{$\leftarrow$confirma?  se sim, pode mostrar isto na
  configuracao abaixo?}\Jbc{added...}

>>>>

Forking OS processes to run test jobs is a popular mechanism of build
systems to obtain parallelism at the machine space (see
Figure~\ref{fig:levels}).  For Java-based systems (e.g., Maven and
Ant), this amounts to spawning one JVM instance (per process) per CPU,
on a machine with potentially many virtual CPUs, and aggregating
corresponding results when jobs finish.  Note that forking can only be
combined with configuration \SeqClassParMeth{} (see
Section~\ref{sec:frameworks}) as Maven only accepts one test class at
a time per forked process.  To attenuate the non-trivial cost of
spawning new processes and JVMs on every test class, Maven offers an
option to reuse the JVM.

%% \Mar{$\leftarrow$Are you sure about this?
%%   It seems silly.  Maybe, the rationale is to ``keep design
%%   simple''.}\Jbc{I'm sure. in addition to keep design simple, I feel
%%   like this was initially conceived to run tests in isolation}

%% \Mar{$\leftarrow$confirma?  se sim, pode mostrar isto na
%%   configuracao abaixo?}\Jbc{added...}
